Simulation pipeline

### 2024-04-11 Analysis/02_Simulation_pipeline.Rmd
added non verbose version of FD:dbFD
 (for cluster runs)

```{r}
## Loading the functions
source("../Functions/melodic.rao.R")
source("../Functions/make.simulation.pipeline.R")
source("../Functions/simulation.pipeline.R")
```

>>>>

```{r}
## Loading the functions
source("../Functions/melodic.rao.R")
source("../Functions/make.simulation.pipeline.R")
source("../Functions/simulation.pipeline.R")
source("../Functions/dbFD.R")
```
